---
title: "Paris - stats"
author: "Maria Prokofieva"
date: "null"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,   
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(skimr)
library(lubridate)
library(leaflet)
theme_set(theme_light())
```



## Paris - airbnb data

This is the exploratory analysis of Paris data available from [InsideAirBNB](http://insideairbnb.com/get-the-data.html)


```{r}
listingsFull<-read_csv("/Users/e5028514/OneDrive - Victoria University/airbnb/paris/dataParisFull.csv")



listing<-read_csv("/Users/e5028514/OneDrive - Victoria University/airbnb/paris/dataParisShort.csv")

#neighbours<-read_csv("/Users/e5028514/OneDrive - Victoria University/airbnb/paris/neighboursFull.csv")

#calendar<-read_csv("/Users/e5028514/OneDrive - Victoria University/airbnb/paris/calendarFull.csv")
```

The data covers the timeframe between


Missing values

```{r}
short<-listingsFull %>%
  select(host_is_superhost,neighbourhood_group_cleansed,review_scores_rating,host_response_time,name,host_since,zipcode, month, price, property_type)

skim(short)


#visna(missingdata,sort="c", mar.col = c("#e06f69","#357b8a"))
```
Missing for 
`host_is_superhost`=`r sum(is.na(missing$host_is_superhost))`

neighbourhood_group_cleansed
review_scores_rating
host_response_time
name
host_since
zipcode


Changes:

`price`: removed $ in front of the number

`month`: calculated from `last_scraped` to month-year format

Number of listings per month

```{r}
listingsFull%>%
  count(month)%>%
  ggplot(aes(month, n))+
  geom_point()+
```


```{r}

head(short)

zipPrices <- short %>% 
  group_by(zipcode, month) %>% 
  summarise(priceAvr = mean(price, na.rm = TRUE))%>%
  arrange(desc(priceAvr))
  

property <-  short %>% 
  group_by(neighbourhood_group_cleansed, property_type) %>% 
  count(property_type, sort=TRUE)

head(property)
#refactor

propertydf <- propertydf %>% filter(property_type %in% c("Apartment","House","Condominium","Townhouse", "Loft"))
totalproperty<-  listingdf %>% filter(property_type %in% c("Apartment","House","Condominium","Townhouse", "Loft"))%>% group_by(neighbourhood_group_cleansed) %>% summarize(sum = n())
propertyratio <- merge(propertydf, totalproperty, by="neighbourhood_group_cleansed")
propertyratio <- propertyratio %>% mutate(ratio = Freq/sum)

```


Number of reviews is used as a proxy for demand
```{r}

calendar <- calendar %>% mutate(booked = ifelse(available=="f", 1, 0))
groupedCalendar <- calendar %>% group_by(date = date) %>% summarise(totalBooked = sum(booked, na.rm = TRUE), totalListings = n()) %>% mutate(percent_booked = (totalBooked/totalListings)*100)
calendarHeat(groupedCalendar$date, groupedCalendar$percent_booked, ncolors = 99, color = "g2r", varname="Occupancy (Percentage) by Month")

```


```{r}
```




dataParis$filename1<-str_extract(dirname(dataParis$filename))

